Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-16 paper/v1.0/sections/5_floquet_drude_conductivity.tex
Corrections appendix
Corrections statrt

A general theory for the conductivity of a dressed system with the disorder averaging was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}. This theory, the general $x$-directional longitudinal DC-limit conductivity has been characterized as
\begin{equation} \label{eq_20}
  \begin{aligned}
    {\sigma}^{xx} &=
    \frac{-1}{4\pi\hbar A}
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon \bigg[
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \\
    & \times
    \tr
    \qty[
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    ]\bigg],
  \end{aligned}
\end{equation}
where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are the $x$-directional electric current operator matrix elements' $0$-th Fourier component and the white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system. Here we have assumed that only $0$-th Fourier component of the current operator is contributing to the conductivity. In addition, $A$ is the area of the considered two-dimensional system, $f$ is the partial distribution function, and $\Pi$ is a function that can be chosen such that
\begin{equation} \label{eq_21}
    \Pi- \frac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \Pi + \frac{\hbar \omega}{2}.
\end{equation}
Here $ \varepsilon_N$ are quasienergies of all relevant Floquet states, and $tr[\cdot]$ is the trace of the considering operator.

@@

We can diagonalize the impurity averaged Green's functions using a unitary transformation ($\vb{T}  \equiv \ket{n,k_x}$) as mentioned in Refs.~\cite{wackerl20,wackerlthesis20,tsuji08}. Thus, we evaluate the matrix elements of the difference between retarded and advanced Green's functions as

@@

    {\sigma}^{xx} & =

@@

@@

with $\tilde{{\Gamma}}(\varepsilon_n,k_x) \equiv \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$. Since we already identified that the inverse scattering time matrix's central element is independent of $k_x$ value, we can drop the $k_x$-dependent in the $\tilde{{\Gamma}}(\varepsilon_n,k_x)$ terms and get the sum over all available momentum space in $x$ direction.

@@

where $X_F \equiv ({\varepsilon_F}/{\hbar \omega_0} - {1}/{2})$

@@

$\gamma_n \equiv {\tilde{{\Gamma}}(\varepsilon_n)}/{\hbar \omega_0}$.

>>>>

A general theory for the conductivity of a dressed system with the disorder averaging was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}. This theory, the general $x$-directional longitudinal DC-limit conductivity has been characterized as
\begin{equation} \label{eq_20}
  \begin{aligned}
    {\sigma}^{xx} =&
    \frac{-1}{4\pi\hbar A}
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon \bigg[
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \\
    & \times
    \tr
    \qty[
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    ]\bigg],
  \end{aligned}
\end{equation}
where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are the $x$-directional electric current operator matrix elements' $0$-th Fourier component and the white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system. Here we have assumed that only $0$-th Fourier component of the current operator is contributing to the conductivity. In addition, $A$ is the area of the considered two-dimensional system, $f$ is the partial distribution function, and $\Pi$ is a function that can be chosen such that
\begin{equation} \label{eq_21}
    \Pi- \frac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \Pi + \frac{\hbar \omega}{2}.
\end{equation}
Here $ \varepsilon_N$ are quasienergies of all relevant Floquet states, and $tr[\cdot]$ is the trace of the considering operator.

@@

We can diagonalize the impurity averaged Green's functions using a unitary transformation ($\vb{T}  = \ket{n,k_x}$) as mentioned in Refs.~\cite{wackerl20,wackerlthesis20,tsuji08}. Thus, we evaluate the matrix elements of the difference between retarded and advanced Green's functions as

@@

@@

    \frac{e^4B^2}{{{m_e}^2}} &

@@

with $\tilde{{\Gamma}}(\varepsilon_n,k_x) = \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$. Since we already identified that the inverse scattering time matrix's central element is independent of $k_x$ value, we can drop the $k_x$-dependent in the $\tilde{{\Gamma}}(\varepsilon_n,k_x)$ terms and get the sum over all available momentum space in $x$ direction.

@@

where $X_F = ({\varepsilon_F}/{\hbar \omega_0} - {1}/{2})$

@@

$\gamma_n = {\tilde{{\Gamma}}(\varepsilon_n)}/{\hbar \omega_0}$.
